\documentclass[11pt, a4paper, roman]{moderncv}

\moderncvtheme[blue]{banking}
\nopagenumbers
\usepackage[utf8]{inputenc}
\usepackage[scale=0.9]{geometry}
\usepackage{multicol}

\newcommand{\project}[5]{
	\textbf{#1}\ifx\&#2\&{}
	\else
    		\href{#2}{\:\small\faGithub\:}\fi$|$ #3
	\hfill\textit{#4}
	#5
	\vspace{2mm}
}

\newcommand{\entry}[4]{
	\textbf{#2}\:$|$\:#1 
	\hfill\textit{#3}
	#4
	\vspace{2mm}
}

\newcommand{\education}[5]{
	\textbf{#1} $|$ #2
	\hfill#3
	\\\textit{#4}
	#5
	\vspace{2mm}
}

\name{Zach}{Sahlin}
\email{zach@sahlins.net}
\mobile{206-607-7655}
\social[github]{GoneSahlin}
\social[linkedin]{zach-sahlin}
\begin{document}
\maketitle
\vspace*{-10mm}
\vspace*{-2mm}
\section{EDUCATION}
\education{Gonzaga University}{Spokane, WA}{August 2019 -- May 2023}{BS in Computer Science, Minor in Applied Mathematics}
{\begin{itemize}
\item Graduated Magna Cum Laude
\item President's List: 3 semesters, Dean's List: 4 semesters
\end{itemize}}
\vspace*{-2mm}
\section{PROJECTS}
\project{Machine Learning for Real Estate}{None}{Python, SQL, PyTorch, JS, Fast API}{Fall 2022 - Spring 2023}
{\begin{itemize}
\item Senior Design Project
\item Collects data on historical rental prices, crime data, and school scores.
\item Predicts future rental prices with an LSTM.
\item Leverages a REST API to connect the web app to the mySQL database.
\item Displays historical prices and predictions as a web app.
\end{itemize}}
\project{Stock Predictor}{https://github.com/GoneSahlin/StocksAI}{Python, TensorFlow, AWS Lambda, AWS EventBridge, selenium}{Spring 2023}
{\begin{itemize}
\item Collects historical and current data from various sources using APIs and web scraping.
\item Stores and retrieves data on AWS S3.
\item Uses an LSTM to predict weekly percentage increase.
\item Displays predictions on a web app.
\item Utilizes GitHub Actions for a CI/CD pipeline to test and publish to AWS Lambda.
\end{itemize}}
\project{Image Resizing CDN}{None}{Python, AWS CloudFront, AWS Lambda, AWS S3, AWS CDK}{Fall 2023}
{\begin{itemize}
\item Automatically resizes, reformats, and caches images using AWS Lambda and AWS CloudFront.
\item Uses AWS CDK to deploy the stack.
\end{itemize}}
\vspace*{-2mm}
\section{RESEARCH}
\project{Long Span Truss Analysis and Optimization}{None}{MATLAB}{Spring 2023}
{\begin{itemize}
\item Worked with Dr. Sara Ganzerli and civil engineering students.
\item Developed a script to analyze and optimize a truss to minimize material use within the load constraints.
\end{itemize}}
\vspace*{-2mm}
\section{WORK EXPERIENCE}
\entry{Gonzaga University}{Teaching Assistant}{August 2022 -- May 2023}
{\begin{itemize}
\item Teaching assistant for Operating Systems, Computer Security, and Internet of Things.
\item Graded programming and written assignments.
\end{itemize}}
\entry{iD Tech}{Online Private Instructor}{June 2021 -- August 2022}
{\begin{itemize}
\item Tutored in 8 different computer science topics, including C++, Java, and Python.
\item Completed over 200 private lessons.
\item Formed relationships with long-term clients, and developed further skills in communication and coding.
\item Collaborated with other instructors to improve teaching methods.
\end{itemize}}
\begin{multicols}{2}
\section{RELATED COURSEWORK}
{\begin{itemize}
\item Algorithms \& Abstract Data Structures
\item Machine Learning \& Intelligent Systems
\item Data Science Algorithms
\item Operating Systems
\item Database Management Systems
\item Programming Languages \& Compilers
\item Linux \& DevOps
\item Natural Language Processing
\end{itemize}}
\columnbreak
\section{TECHNICAL SKILLS}
{\begin{itemize}
\item Languages: C++, Java, Python, C, SQL
\item Tools: Git, Linux, Docker, Jupyter, GitHub Actions, Postgres, AWS Lambda, AWS S3Libraries: TensorFlow, PyTorch, pandas, NumPy, scikit-learn, Matplotlib
\end{itemize}}
\end{multicols}
\end{document}